Sr: Processing Data Streams and Avoiding Work

### 2012-05-04 paper/paper.tex
Hard wrap lines in tex source

\title{Sr: Processing Data Streams By Doing Less Work}
\author{Ryan Lopopolo\\
\texttt{lopopolo@mit.edu}}

@@

Fetchers can fail. The only consequence of fetcher failure is that some of the input stream is lost forever. Since streams contain much data and are likely stored permanently elsewhere on disk, Sr does not attempt to recover this data.

Worker failures may entail some lost work. Having the master poll each worker frequently for its progress mitigates the consequences of worker failure. For jobs that run for minutes or hours, 100ms of lost work is << 0.1% of the total. Sr can simply treat these lost tasks as preemptively killed, which is already expected by the cluster.

@@

\begin{figure}
\begin{verbatim}
                  |--------|
                - | worker |
               /  |--------|
|-----------| /   |--------|
| master    | --- | worker |
| spout     |     |--------|
| fetcher   |     |--------|
| collector | --- | worker |
|-----------| \   |--------|
               \  |--------|
                - | worker |
                  |--------|

\end{verbatim}
\caption{Topology of the test Sr cluster. Each box is a single machine.}
\label{fig:clusterDiagram}
\end{figure}

@@

To serve the data, I munged it into a YAML file containing a hash of \lstinline[language=Ruby]{article_id : fulltext}. To store fulltext, I base64 encoded it and deflated it. This requires workers to inflate and decode the fulltext before they can process it further. The server reads from this YAML file and returns the resulting hash as JSON.

@@

\begin{figure}
\includegraphics[width=\linewidth]{long-tail-ranks.png}
\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-tailed distribution.}
\label{fig:wordDist}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{f-score.png}
\caption{$F_{0.5}$-score for the top-100 word count job. I measured the $F$-score with $\beta = 0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more about precision than recall.}
\label{fig:fscore}
\end{figure}

@@

Table~\ref{table:runtime} shows the effect of varying the kill rate and work level. The row with kill rate = 0.0 and work level = 1.0 represents the perfect, MapReduce-style, execution of the word count job. The only consistent reduction in execution time is a result of increasing the kill rate. Increasing the kill rate exhibits a linear reduction in execution time as the fraction of processed data linearly decreases.

\begin{table}
\begin{tabularx}{\linewidth}{|X|X|X|}
\hline
Kill rate & Work level & Avg. execution time [minutes] \\ \hline
0.0 & 1.0 & 11:35.5 \\ \hline
0.0 & 0.4 & 10:33.8 \\ \hline
0.0 & 0.8 & 10:30.8 \\ \hline
0.2 & 0.4 & 08:25.8 \\ \hline
0.2 & 0.8 & 08:37.8 \\ \hline
0.4 & 0.4 & 06:54.0 \\ \hline
0.4 & 0.8 & 06:28.2 \\ \hline
0.6 & 0.4 & 04:14.7 \\ \hline
0.6 & 0.8 & 04:13.7 \\ \hline
0.8 & 0.4 & 02:33.3 \\ \hline
0.8 & 0.8 & 02:15.0 \\ \hline
\end{tabularx}
\caption{Impact of kill rate and work level on job execution time.}
\label{table:runtime}
\end{table}

>>>>

\title{Sr: Processing Data Streams and Avoiding Work}
\author{Ryan Lopopolo\\
\texttt{lopopolo@mit.edu}}

@@

Fetchers can fail. The only consequence of fetcher failure is that some of the input stream is
lost forever. Since streams contain much data and are likely stored permanently elsewhere on disk
Sr does not attempt to recover this data.

Worker failures may entail some lost work. Having the master poll each worker frequently for its
progress mitigates the consequences of worker failure. For jobs that run for minutes or hours,
100ms of lost work is << 0.1\% of the total. Sr can simply treat these lost tasks as preemptively
killed, which is already expected by the cluster.

@@

\begin{figure}
\begin{verbatim}
                  |--------|
                - | worker |
               /  |--------|
|-----------| /   |--------|
| master    | --- | worker |
| spout     |     |--------|
| fetcher   |     |--------|
| collector | --- | worker |
|-----------| \   |--------|
               \  |--------|
                - | worker |
                  |--------|
\end{verbatim}
\caption{Topology of the test Sr cluster used in the word count case study.\\
Each box is a single machine.}
\label{fig:clusterDiagram}
\end{figure}

@@

To serve the data, I munged it into a YAML file containing a hash of
\lstinline[language=Ruby]{article_id : fulltext}. To store fulltext, I base64 encoded it and
deflated it using zlib. This requires workers to inflate and decode the fulltext before they
can process it further. The server reads from this YAML file and returns the resulting hash as
JSON.

@@

\begin{figure}
\includegraphics[width=\linewidth]{long-tail-ranks.png}
\caption{The frequencies of words in the Wikipedia Featured Articles corpus\\
have a long-tailed distribution.}
\label{fig:wordDist}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{f-score.png}
\caption{$F_{0.5}$-score for the top-100 word count job. I measured the $F$-score with\\
$\beta=0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more\\
about precision than recall.}
\label{fig:fscore}
\end{figure}

@@

Table~\ref{table:runtime} shows the effect of varying the kill rate and work level. The row
with kill~rate~=~0.0 and work~level~=~1.0 represents the perfect, MapReduce-style, execution
of the word count job. The only consistent reduction in execution time is a result of
increasing the kill rate. Increasing the kill rate exhibits a linear reduction in execution
time as the fraction of processed data linearly decreases.

\begin{table}
\begin{tabularx}{\linewidth}{|X|X|X|}
\hline
Kill rate & Work level & Average execution time [minutes] \\ \hline
0.0 & 1.0 & 11:35.5 \\ \hline
0.0 & 0.4 & 10:33.8 \\ \hline
0.0 & 0.8 & 10:30.8 \\ \hline
0.2 & 0.4 & 08:25.8 \\ \hline
0.2 & 0.8 & 08:37.8 \\ \hline
0.4 & 0.4 & 06:54.0 \\ \hline
0.4 & 0.8 & 06:28.2 \\ \hline
0.6 & 0.4 & 04:14.7 \\ \hline
0.6 & 0.8 & 04:13.7 \\ \hline
0.8 & 0.4 & 02:33.3 \\ \hline
0.8 & 0.8 & 02:15.0 \\ \hline
\end{tabularx}
\caption{Impact of kill rate and work level on job execution time.}
\label{table:runtime}
\end{table}
